Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-31 scagnostics.Rmd
Acknowledgements update.

# Acknowledgments {-}
We thank Rory Smith for help with the gravitational wave examples, and German Valencia for useful comments.

>>>>

# Acknowledgments {-}
The authors gratefully acknowledge the support of the Australian Research Council.
We thank Rory Smith for help with the gravitational wave examples, and German Valencia for useful comments.
This article was created with knitr [@knitr], R Markdown [@rmarkdown] and bookdown [@bookdown] with embedded code.
